\subsection{Audio module analysis}
The audio generation is very processor heavy - if more than monophonic
bleeps are desired that is. - To produce alias free audio in the full audible
range, the output has to be updated more than 40000 times a second.
Therefore this task is moved from the \emph{eZ8} to a \emph{Texas
Instruments} \emph{Stellaris Launchpad}, an evaluation-board for the 80MHz
\emph{ARM Cortex-4M} \emph{LM4F120H5QR} chip.
%TODO tilføj link til http://www.ti.com/tool/EK-LM4F120XL

The \emph{LM4F120H5QR} is ideal as:
\begin{itemize}
  \item It has 64kB of FLASH memory, enough for a medium-size program and small
  wave-files;
  \item 32 bit fixed point processor, providing a solid frame for fast and
  precise generative sound synthesis;
  \item build in PWM module that width some external filtering can be used a a
  digital to analog converter, removing the need for an external ADC. Furthermore
  the output is powerful enough to drive small headphones at low volumes.
  \item We have past experience with the processor and associated tools, thus
  the time cost can be reduced by choosing this solution over another.
  
\end{itemize}

As the audio module has to play both a piece of music and sound-effects; a mix
of generated sounds and playback of wave-files is chosen.

The use of generated music cuts down the space a huge wave-file would take. 10s
of 8bit data at 44kHz is 0.44MB, we can't fit that in the 64kB FLASH of the
\emph{LM4F120}. On the other hand even at 80MHz speech synthesis becomes
troublesome, but if speech is re-sampled to ~10kHz it is still possible to make
out words. Percussion sounds can also be put in down-sampled wave-files, as
aliasing artifacts aren't a huge sacrifice when dealing with short, rhythmic
outbursts.


