\section{Conclusion}
We have created an arkanoid clone, named Smashing Bricks, that runs on an eZ8 microcontroller
 development board and communicates with a Stellars Launchpad microcontroller to produce sound effects
that go along with the game. The software has been designed to be modular and
easily extensible. We believe we have succeeded in this, since modules are self contained, 
and provide a few well defined entry points for other modules to use. The final game has
the following features:
\begin{itemize}
	\item Continuously calculated reflection angle from the striker.
	\item Bricks with any number of lives, colored after this number.
	\item Background music.
	\item Sound effects.
	\item ASCII art backgrounds generated from real pictures.
	\item Analog joystick input.
	\item A score system.
	\item Multiple levels.
	\item Limited number of player lives.
	\item 30 frames per second graphics.
\end{itemize}
Which is all but the two lowest priority items on our wanted feature list. The developed API and application code
would allow for these features being added with only minor changes to the existing code. \\

Using rendering optimizations we have circumvented some of the I/O bottlenecks that were a limiting factor in the
design. We have not had any performance issues with code that does not make use of I/O and as such we are
able to run the game at a constant framerate of 30 frames per second. \\

Tests have been performed both on the audio modules and game modules. Although these tests were manual and
not automated, they were still adequete to insure that the game is working as intended. However rare
edge cases may not have been recognised.

