\section{Design}
This section covers both game design and software architecture design, as well as the
design of the individual software modules.

\subsection{Game Design}
The game is an arkanoid clone and as such it is very simple and follows the general arkanoid formula of destroying
bricks using a ball that bounces around the screen. The ball will reflect itself off of a brick, wall
in the top of the playing space as well as two walls bordering the sides of the playing space.
There is nothing stopping at the bottom of the playing space, except the player controlled striker.
It is the players objective to control the striker such that the ball is reflected off of it and
hits all the bricks. Thereby destroying the bricks. \\

In this version of arkanoid, which we will henceforth refer to as Smashing Bricks, the player
upon starting a game is presented with a splash screen, followed by the first level. The levels
themselves contain a brick layout that can be changed as well as a monochrome background image.
Upon completion of the level, the full-color background image is revealed and the player can
move on to the next level. Once the player reaches the end of the game, the players score
will be presented and the option to restart the game will be available. \\

The score is incremented by a set amount every time a brick is hit or destroyed. If the player
misses the ball, another amount is subtracted from the score. If the players score goes below
0, the game is over and the player will have the option to restart the game. \\

The balls reflection from the striker is not actually a reflection, instead the direction
of the ball is changed according to where it hit the striker. As with all games, these
mechanics are based on their feeling and this to us felt like the most natural way to play.
Similarly the speed of the ball and striker are also based on feel. \\

Background music will play and sound effects are triggered every time the ball is reflected
from a brick, a wall or the striker. \\

The game only has a single difficulty, hard, this is due to the fact that we deemed slow and/or
easy arkanoid games to get boring too quickly. The game is therefore deliberately designed to 
force the player to quickly be able to estimate where the ball will reach the bottom again, as 
soon as it leaves the striker.

\subsection{Software Architecture Design}
